---
title: "index"
author: "Simon"
date: "24 1 2018"
output: 
  #github_document
  html_document:
    self_contained: no
---

<!-- <style> -->
<!-- body .main-container { -->
<!--     max-width: 50%; -->
<!-- } -->
<!-- </style> -->


<style type="text/css">
body .main-container {
    max-width: 50%;
}
body{ /* Normal  */
      font-size: 14px;
  }
td {  /* Table  */
  font-size: 8px;
}
h1.title {
  font-size: 38px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 28px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 22px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 14px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>



```{r, echo=FALSE, message=FALSE, fig.height=.1}
source("helpers.R")
library(shiny)
library(shiny.semantic)
shiny.semantic::uirender(tagList(sidebar()))
```

**Note:** this is personal summary.

The repository directory to this static html file is built as follows:

```{r, echo = FALSE, message = F}
#source("src/sidebar.R")
shiny.semantic::uirender(tagList(repo_structure()))
```


# Intro

# Basic

# YAML

<br>
<br>
<br>
<br>
<br>

# Output Formats

<br>
<br>
<br>
<br>
<br>

# Interactive Visuals

## Highcharter
<br>
<br>
<br>
<br>
<br>

# UI Extensions

## Semantic UI
<br>
<br>
<br>
<br>
<br>
